---
title: "Drill Through the Earth"
author: "Kevin Wagg"
date: "February 4, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Haven't you always...

Haven't you always wondered what life would be like if you were on the opposite side of the earth?

## Can't go there

We can't take you there, but we can show you exactly where it is.  You just have to:

- Navigate to: https://kevinw7.shinyapps.io/OppositeSide/
- Enter an address
- Click 'Submit'

## How does it do that?
Our app uses the Google Geocode api to retrieve the longitude and latitude of the entered address.  Our app shows the address on a map using leaflet.  It then calculates the location on the opposite side of the Earth and maps that.

## Some code

```{r initalize, echo = FALSE, message = FALSE, warning = FALSE}

library(shiny)
library(RCurl)
library(RJSONIO)
library(plyr)

    url <- function(address, return.call = "json", sensor = "false") {
        root <- "http://maps.google.com/maps/api/geocode/"
        
        u <- paste(root, return.call, "?address=10 Downing Street, London England", address, "&sensor=", sensor, sep = "")
        return(URLencode(u))
    }
```

Below are the results of calling the Google geocode api with the home address of the Prime Minister of England, 10 Downing Street, London England:

```{r continue, echo = FALSE, message = FALSE, warning = FALSE}    
    geoCode <- function(address,verbose=FALSE) {
        if(verbose) cat(address,"\n")
        u <- url(address)
        doc <- getURL(u)
        x <- fromJSON(doc,simplify = FALSE)
        if(x$status=="OK") {
            lat <- x$results[[1]]$geometry$location$lat
            lng <- x$results[[1]]$geometry$location$lng
            location_type <- x$results[[1]]$geometry$location_type
            formatted_address <- x$results[[1]]$formatted_address
            return(c(lat, lng, location_type, formatted_address, u))
        } else {
            return(c(NA,NA,NA, NA))
        }
    }
    
    myResult <- function() {
        return(geoCode("10 Downing Street, London England"))
    }
    
    myResult()[[5]]
    lat = paste("Latitude: ", as.numeric(myResult()[[1]]))
    lng = paste("Longitude: ", as.numeric(myResult()[[2]]))
    lat
    lng
```

